---
title: "Kurumada"
author: "Will Clapp"
date: "5/26/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(pwr)
library(lme4)
library(patchwork)
library(languageR)
library(MuMIn)
library(car)
library(powerMediation)

```

```{r}
df.neg_subj_info <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/experiment_negative_shift/mturk/experiment-subject_information.csv")

df.no_subj_info <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/experiment_no_shift/mturk/experiment-subject_information.csv")

df.subj_info <- bind_rows(df.neg_subj_info, df.no_subj_info)
```



```{r}
# df.neg_shift <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/experiment_negative_shift/mturk/experiment-trials.csv")
# df.no_shift <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/experiment_no_shift/mturk/experiment-trials.csv")
# df.data <- bind_rows(df.neg_shift, df.no_shift)
# df.trials <- df.data %>%
#   filter(affirmative_cont == "none")
# df.trials <- df.trials %>%
#   mutate("response_01" = ifelse(response == "target", 1, 0))
# 
# # mutate to center continuum steps
# df.trials = df.trials %>% 
#   mutate("cStep" = continuum_step - mean(continuum_step))
# # 
# write.csv(df.trials, "/Users/willclapp/Desktop/245B/Replication245B/analysis/csvs/trials.csv")


df.trials <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/analysis/csvs/trials.csv")

df.my_stims <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/analysis/csvs/my_stims.csv")
df.original_stims <- read.csv("/Users/willclapp/Desktop/245B/Replication245B/analysis/csvs/original_stims.csv")

```




Visualize trial breakdown, original and new

```{r}
p1 = ggplot(data = df.original_stims,
       mapping = aes(x = step,
                     y = instances)) +
  geom_col(aes(fill = follow)) +
  facet_grid(cols = vars(condition)) +
  theme_bw() +
  labs(title = "Original distribution of exposure stimuli",
       x = "Continuum step (noun-focus to verb-focus)",
       y = "Number of exposure trials") +
  scale_fill_manual(name = "Continuation phrase", 
                      labels = c("Affirmative", "Negative"),
                      values = c("#1d87b8", "#b31010")) +
  scale_x_continuous(limits = c(0,13), breaks = c(seq(1, 12, 3), 12)) +
  theme(legend.position = 'none')
  

p2 = ggplot(data = df.my_stims,
       mapping = aes(x = step,
                     y = instances)) +
  geom_col(aes(fill = follow)) +
  facet_grid(cols = vars(condition)) +
  theme_bw() +
  labs(title = "New distribution of exposure stimuli",
       x = "Continuum step (noun-focus to verb-focus)",
       y = "Number of exposure trials") +
  scale_fill_manual(name = "Continuation phrase", 
                      labels = c("Affirmative", "Negative"),
                      values = c("#1d87b8", "#b31010")) +
  scale_x_continuous(limits = c(0,17), breaks = c(seq(1, 16, 3)))

p1+p2


```


```{r}

df.test_good <- df.trials_good %>% 
  group_by(group, continuum_step) %>% 
  summarise(response = mean(response_01)) 


```



```{r}
ggplot(data = df.test_good,
       mapping = aes(x = continuum_step,
                     y = response,
                     color = group)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_bw() +
  scale_x_continuous(limits = c(1, 16),
                     breaks = seq(2,16, by = 2)) +
  labs(y = "Proportion of target response",
       x = "Continuum step") 
  scale_color_manual(name="Condition", values = c("#1d87b8", "#b31010")) 
  # scale_fill_manual(name = "Continuation phrase", 
  #                     labels = c("Affirmative", "Negative"),
  #                     values = c("#1d87b8", "#b31010")) 

  



```






```{r}
glm.trials = glm(response_01 ~ 1 + group * cStep, 
                     data = df.trials_good,
                     family="binomial")

summary(glm.trials)
```

```{r}
glmer.simple = glmer(response_01 ~ 1 + cStep + (1 | item), 
                     data = df.trials_good,
                     family="binomial")

summary(glmer.simple)

```

```{r}

glmer.trials = glmer(response_01 ~ 1 + group * cStep + (1 | item), 
                     data = df.trials_good,
                     family="binomial")


summary(glmer.trials)

anova(glmer.simple, glm.trials)


vif(glmer.trials)
```

So, for group, beta = 0.48, SE = 0.12, p < 0.001. And for step, beta = -0.08, SE = 0.02, p < 0.001. Positive value is target, negative is competitor.




Filter out participants who messed up steps 2 & 4
```{r}
df.bad <- df.trials %>% 
  filter(continuum_step == 2|continuum_step == 4) %>% 
  group_by(participant_id) %>% 
  summarise(response = mean(response_01)) %>% 
  filter(response == 0)

df.good <- df.trials %>% 
  filter(continuum_step == 2|continuum_step == 4) %>% 
  group_by(participant_id) %>% 
  summarise(response = mean(response_01)) %>% 
  filter(response != 0)

df.trials_bad = df.trials %>% 
  filter(participant_id %in% df.bad$participant_id)

df.trials_good = df.trials %>% 
  filter(participant_id %in% df.good$participant_id)


```



```{r}
mean(df.trials$Answer.time_in_minutes)

```







